\cvsection{Experience}
\begin{cventries}
  \cventry
    {Senior Cybersecurity Engineer}
    {Southwest Airlines}
    {Dallas, Texas}
    {August 2018 - Present}
    {
      \begin{cvitems}
        \item {Building a modern Identity solution for 100M+ Southwest.com customers.}
        \item {Migrated a legacy login solution for the Enterprise to a new Identity Provider enabling 70,000+ employees with SSO and MFA across hundreds of onboarded applications.}
        \item {Previously worked on the Cybersecurity Operations team, fulfilling requests and solving incidents related to all of Southwest's Cybersecurity technologies.}
      \end{cvitems}
    }
  \cventry
    {Mac+ Technical Advisor}
    {Apple}
    {Athens, Georgia}
    {September 2016 - May 2018}
    {
      \begin{cvitems}
        \item {Provided technical support for all iOS, watchOS, and macOS devices and related hardware, software and accessories.}
        \item {Solved identity and access incidents related to user Apple ID, iCloud, and iTunes accounts.}
      \end{cvitems}
    }  
  \cventry
    {IT Asset Management - Intern}
    {Equifax}
    {Alpharetta, Georgia}
    {August 2017 - May 2018}
    {
      \begin{cvitems}
        \item {Developed a program to teach an existing software library qualitative information about unrecognized software installed on company assets managed by the IT Asset Management team.}
        \item {Acted as project manager for this Engineering Capstone project at the University of Georgia.}
      \end{cvitems}
    }
  \cventry
    {IT Intern}
    {INP North America}
    {Alpharetta, Georgia}
    {August 2013 - August 2014}
    {
      \begin{cvitems}
        \item {Served as an apprentice to the IT department and provided local and remote tier-1 tech support for office IT infrastructure and employee assets.}
        \item {Automated common employee Microsoft Office tasks in VisualBasic, specifically Excel and PowerPoint.}
      \end{cvitems}
    }
\end{cventries}